Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-06-15 index.Rmd
wordsmithing

This compendium details the statistical analysis and methods while undertaking a meta-analysis of fungicide efficacy trials for control of powdery mildew in mungbean. 
This meta-analysis will focus on the main aim of:

> When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?

>>>>

This compendium details the statistical analysis and methods while undertaking a meta-analysis of fungicide efficacy trials for control of powdery mildew in mungbean. 
This meta-analysis will focus on the main aim of determining:

> When is the optimum time to spray fungicide to limit the effect of powdery mildew on mungbean yields?
